
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

This code uploads the ~250 attribute files to DB tables which I hope is more efficient than doing it manually
by running the "import to server.bat" file.

This code 
1. Empties the att.XXXX tables in the data base.  DANGER
1. Copies files from the individual group folders
2. loops over each of the attributes group folder and uploads the csv file to the DB using the appropriate sql package.

The code will stop if the column headings of file bp_date_reading.csv are incorrect.

To do:
1. Get this code to generate a pdf!
1. Need R code to write errors to one file and not 250!!!
2. Check that the number of rows on disk is the same as the number of rows in DB table

IMPROVEMENT:
1. Use the import_attributes.bat to read in the names of the files that need to be uploaded.
Currently I create the string with each filename in to execute the upload package.  But if I
use the bat file then the bat file will also be checked to be correct.  Butttt the way it is
done currently is better because it ensures that for each attribute that it exists and that
there is an associated dtsx file.  Thinking.

Use at the command prompt:
where dtexec.exe
to find the location of DTEXEC.exe which is the executable we need to upload files to DB using the SQL packages.


```{r init}
library(tidyverse)
library(assertthat)
library(odbc)
library(DBI)
library(logger)
```

```{r definitions} 
thisMonth = "202202"
folder_names = c("All_Groups","Group_One", "Group_Two", "Group_Three", "Group_Four", "Group_Five", "Group_Six", "Group_Seven")
attributes_path = paste0("Z:\\Population Health Management\\Attributes Data\\processing_folder\\Raw_Data\\", thisMonth)
pathToPackage = "Z:/Population Health Management/Attributes Data/processing_folder/sql_packages/"
pathToExec="C:\\Program Files (x86)\\Microsoft SQL Server\\120\\DTS\\Binn\\DTEXEC.exe"
importToServerFolder = "Z:/Population Health Management/Attributes Data/processing_folder/import_to_server/"
```
 
 
```{r clearAttributeTables}
ans = readline("Would you like to clear the attribute database tables in Population_Segmentation? (EXEC sp_EmptyTables).  \nClose VPN connection now if it is open.  Enter Y or N.")
if (ans=="Y") { # make a connection to DB and execute code
  tryCatch( {
    message("Trying to connect to database.")
    con <- dbConnect(odbc(), 
                   Driver = "SQL Server", 
                   Server = "ocdb01", 
                   Database = "Population_Segmentation", 
                   Trusted_Connection = "True")
  }, error=function(cond) {
    message("Connection to database failed.")
    message(cond)
    return(NA) 
  }, finally={
    message("Connection to database success.")
    log_info(con)
  })
  # Execute stored procedure
  log_info("Running EXEC sp_EmptyTables ... takes a few moments....")
  out = dbExecute(con, "EXEC sp_EmptyTables")
  assert_that(are_equal(out,0), msg="Emptying the attribute tables may have failed.  Investigate.  Try re-running.")
  log_info(out)
  log_info("Emptied the contents of the attribute tables.")
  dbDisconnect(con)
}  
```

Perform upload of one file.
This is used when there is a problem.
*** Do not execute in normal circumstances ***
If out is 1 then the upload has failed and the code will stop.  We need out to be 0 to define success.
Remember: DELETE FROM att.adhd 
DELETE FROM att.adhd
```{r uploadOneFile, eval=FALSE}
Do not run this.  For use when there is a problem
pathToPackageX = paste0('"', pathToPackage, gsub(".csv", ".dtsx", "hba1c.csv"), '"')
out = system2(pathToExec, paste0('-File ', pathToPackageX),
         stdout = 'stdout.txt', stderr = 'stderr.txt', wait = TRUE)
assert_that(out==0, msg=paste0("Upload failed for", pathToPackageX, "."))
```

We loop over each of the 8 directories (Group 1 to Group 7 and all groups) and upload each csv file
in those directories.  Previous code checks (PHM_Validate_X.Rmd) that all the csv files are there and are valid (no header file,
greater than 0 KB etc).

The code copies files from the individual group directories and paste them to folder "import to server".
In this loop we loop over each of the 8 group folders and upload each csv attribute file to the DB.
If an attribute fails to upload then 
1. Open it up in Excel and check it.
2. Download the file again from EMIS.
3. Rebuild the dtsx file
```{r performUpload}
# Check that folder import to server is empty before we copy anything into it.  If it isn't empty
# then delete the csv in it.
dataFiles = dir(importToServerFolder, pattern="\\.csv$", ignore.case = FALSE, all.files = FALSE)
if (length(dataFiles)>0) {
   out = file.remove(paste0(importToServerFolder, dataFiles))
}
nGroups = length(folder_names)
    
for (j in 1:nGroups) {
#for (j in 1:1) {l
  indGroupFolder = paste0(attributes_path,"\\", folder_names[j])
  dataFiles = dir(indGroupFolder, pattern="\\.csv$", ignore.case = FALSE, all.files = FALSE)
  # Make sure that at least 20 files copied to the import to server folder
  assert_that(length(dataFiles)>=20, msg=paste0("Less than 20 files in the folder ", folder_names[j]))
  # Copy files to folder "importToServer"
  log_info("Copying files to folder import to server...")
  file.copy(from=paste0(indGroupFolder,"\\",dataFiles), to=importToServerFolder, overwrite = TRUE)
  
  
  listOfAttributes = list.files(paste0(attributes_path,"\\", folder_names[j]), pattern="\\.csv$") # \\.csv$
  nFiles = length(listOfAttributes)
  
  for (i in 1: nFiles) {
    fullAttributePath = paste0(attributes_path,"\\", folder_names[j],"\\", listOfAttributes[i])
    aFile = listOfAttributes[i]
    
    # Don't upload these files while Harry looks into a problem with the packages.
    # THIS SHOULD BE REMOVED.  Harry wants to upload these ones manually.
    #if (aFile == "Referral to social prescribing service.csv" |
    #     aFile == "Social prescribing declined.csv" |
    #     aFile == "Social prescribing offered.csv") {
    #     message("Cycling....")
    #     next
    #}
    # It took a loooong time to workout that I needed to put quotes around the paste in order
    # for System2 command to work
    # check I can open package (they are text files).  This captures if it exists or not.
    # *** Harry and I made changes to the package names.  Be vigilent. ***
    if (aFile=="hba1c_1.csv") {
        pathToPackageX = paste0('"', pathToPackage, "hba1c_g1_1.dtsx", '"')
        packData = read.csv(paste0(pathToPackage, "hba1c_g1_1.dtsx"))
    } else if(aFile =="hba1c_2.csv") {
      pathToPackageX = paste0('"', pathToPackage, "hba1c_g1_2.dtsx", '"')
      packData = read.csv(paste0(pathToPackage, "hba1c_g1_2.dtsx"))
    } else if(aFile =="idh_nonmi.csv") {
      # typo on condition idh_nonmi.csv but ihd_nonmi.dtsx
      pathToPackageX = paste0('"', pathToPackage, "ihd_nonmi.dtsx", '"')
      packData = read.csv(paste0(pathToPackage, "ihd_nonmi.dtsx"))
    } else {
       pathToPackageX = paste0('"', pathToPackage, gsub(".csv", ".dtsx", aFile), '"')
       packData = read.csv(paste0(pathToPackage, gsub(".csv", ".dtsx", aFile)))
    }
    log_info("File {i} of {nFiles}: uploading file {aFile} in {folder_names[j]} with package {pathToPackageX}")
    # Check I can open csv file
    attribData <- read.csv(fullAttributePath)
    
    
    #print(paste0("Calling package for attribute ", aFile))
    if (aFile == "bp_date_reading.csv") {
      columnNames = colnames(attribData)
      # there must be four headings and they must be:
      m = paste0("Check the column headings in file bp_date_reading.csv in ",  folder_names[j], ".  They need to be Value_sy and Value_di.")
      assert_that(are_equal(columnNames[1], "NHS.Number"), msg=m)
      assert_that(are_equal(columnNames[2], "Date"), msg=m)
      assert_that(are_equal(columnNames[3], "Value_sy"), msg=m)
      assert_that(are_equal(columnNames[4], "Value_di"), msg=m)
    }
    out = system2(pathToExec, paste0('-File ', pathToPackageX),
         stdout = 'stdout.txt', stderr = 'stderr.txt', wait = TRUE)
    
    assert_that(out==0, msg=paste0("The file ", aFile, " has not been correctly uploaded.  Check the stderr.txt and stdout.txt files in this directory."))
    # Check that the stderr.txt is empty and stop if it is not
    stderr <- read_csv("stderr.txt")
    assert_that(are_equal(nrow(stderr),0), msg="The file stderr.txt has an error.  Code terminated.  Take a look at this file.")
    
    # Have a rest every n loops
    if (i %% 100==0) {
        log_info("Resting....")
        Sys.sleep(5) # amount expressed in seconds.
    }
  }
  # We have completed uploading the files from an individual group.  Now delete the files in "import to server"
  # and move to the next group
  log_info("deleting files in folder import to server ...")
  out = file.remove(paste0(importToServerFolder, dataFiles))
  assert_that(are_equal(sum(out!=TRUE),0), msg="Looks like some files were not deleted from the import to server folder.  Perhaps someone has a file open on their machine.")
}

#log_info("Check that the three new metrics from December 2021 have been uploaded into the DB correctly.  You should find #Att.personal_care_plan_completed, Att. preferred_priorities_for_care_document_completed and Att.respect_setting.")
```


Now import the measurement files.

```{r definitions} 
#thisMonth = "202202"
folder_names = c("G1","G2", "G3", "G4", "G5", "G6", "G7")
activity_path = paste0("Z:\\Population Health Management\\Activity Data\\processing_folder\\Raw_Data\\", thisMonth)
pathToPackage = "Z:/Population Health Management/Activity Data/processing_folder/Raw_Data/sql_packages/"
pathToExec="C:\\Program Files (x86)\\Microsoft SQL Server\\120\\DTS\\Binn\\DTEXEC.exe"
importToServerFolderMeasurements = "Z:/Population Health Management/Activity Data/processing_folder/Raw_Data/import_measurements/"
```

Perform measurement uploads.
```{r performUpload}
# Check that folder import to server is empty before we copy anything into it.  If it isn't empty
# then delete the csv in it.
dataFiles = dir(importToServerFolderMeasurements, "\\.csv$", ignore.case = FALSE, all.files = FALSE)
if (length(dataFiles)>0) {
   out = file.remove(paste0(importToServerFolderMeasurements, dataFiles))
}
nGroups = length(folder_names)

for (j in 1:nGroups) {
#for (j in 1:1) {
  indGroupFolder = paste0(activity_path,"\\Measurements\\", folder_names[j])
  dataFiles = dir(indGroupFolder, ignore.case = FALSE, all.files = FALSE, pattern="\\.csv$") #  # \\.csv$
  # Make sure that at least 20 files copied to the import to server folder
  assert_that(length(dataFiles)>=10, msg=paste0("Less than 9 files in the folder ", folder_names[j]))
  
  log_info("Copying files to folder import_measurements...")
  file.copy(from=paste0(indGroupFolder,"\\",dataFiles), to=importToServerFolderMeasurements, overwrite = TRUE)
  
  
  listOfMeasurements = list.files(paste0(activity_path,"\\Measurements\\", folder_names[j]), pattern="\\.csv$") # pattern="*.csv"
  # Here is how to upload one file in case there is every a need.
  #listOfMeasurements = "efi_category.csv"
  nFiles = length(listOfMeasurements)
  message("There are ", nFiles, ' to cycle over.')
  for (i in 1: nFiles) {
    fullMeasurementPath = paste0(activity_path,"\\Measurements\\", folder_names[j],"\\", listOfMeasurements[i])
    aFile = listOfMeasurements[i]
    

    pathToPackageX = paste0('"', pathToPackage, "mea_",gsub(".csv", ".dtsx", aFile), '"')
    packData = read.csv(paste0(pathToPackage, "mea_",gsub(".csv", ".dtsx", aFile)))
    
    log_info("File {i} of {nFiles}: uploading file {aFile} in {folder_names[j]} with package {pathToPackageX}")
   
    measurementData <- read.csv(fullMeasurementPath)
    
    
    out = system2(pathToExec, paste0('-File ', pathToPackageX),
         stdout = 'stdout.txt', stderr = 'stderr.txt', wait = TRUE)
    
    assert_that(out==0, msg=paste0("The file ", aFile, " has not been uploaded correctly.  Check the stderr.txt and stdout.txt files in this directory."))
    # Check that the stderr.txt is empty and stop if it is not
    stderr <- read_csv("stderr.txt")
    assert_that(are_equal(nrow(stderr),0), msg="The file stderr.txt has an error.  Code terminated.  Take a look at this file.")
    
    # Have a rest every n loops
    if (i %% 100==0) {
        log_info("Resting....")
        Sys.sleep(5) # amount expressed in seconds.
    }
  }
  # We have completed uploading the files from an individual group.  Now delete the files in "import_measurements"
  # and move to the next group
  log_info("deleting files in folder import_measurements ...")
  out = file.remove(paste0(importToServerFolderMeasurements, dataFiles))
  assert_that(are_equal(sum(out!=TRUE),0), msg="Looks like some files were not deleted from the import_measurements folder.  Perhaps someone has a file open on their machine.")
}
```

Upload one file:
```{r upload_one_measurement_file}

    out = system2(pathToExec, paste0('-File ', pathToPackageX),
         stdout = 'stdout.txt', stderr = 'stderr.txt', wait = TRUE)
```
