```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
Aim of this code is to 1) read in the metrics file which contains the number of each attributes historically
2) to create a minimum and maximum for each attribute based on that data and 3) to determine if this months'
data falls within that range.

IMPORTANT: it is a good idea to run file determineAcceptableRangesForSubmissionFile.Rmd before executing this code but talk to Philip about this first.  IMPORTANT: the file attribSubmissionVolumes2021 SHOULD NOT include the current months attributes data.

Determine acceptable levels for each metric.  This is done by finding the minimum and maximum value
from the submission considered in this code.

This code does not WRITE data to the database; only reads.

This code outputs two files: areAttributesReadyToSubmit_Actuals.csv and areAttributesReadyToSubmit_Prevalence.csv.
Use Excel to format the Prevalence output file into Percents to make easier reading.  Anything outside the minimum or maximum range needs investigation.

Check that each row has a value of "this month" which falls between the minimum and maximum of the previous n
months.


Done:
1. put this month column towards the end of the table 
2. calculate prevalence
3. minimum greater than 0
4. upload code to github
5. bug fix.  Was calcualting the mean, min, and max including this month when it should have excluded this month.

```{r init}
library(tidyverse)
library(lubridate)
library(odbc)
library(DBI)
library(stringi)
library(assertthat)
library(scales)
source("processASubmissionFile.R")
```

These inputs are the only place in the code where you need to change variables from one month to the next.
```{r inputs}
# Assumes the schema is "terminal"
thisMonthsSubmissionDBTable = "attrib_202107_complete"
comparisonFile = "./AttributeSubmissionVolumes/attribSubmissionVolumes2021-08-13_Master.csv"
```

Read in attribute file which gives us the number of records per submission for each attribute.
```{r readsubmissionVolumes}
submissionVolumes = read.csv(comparisonFile, stringsAsFactors = FALSE)
```



Now get this months attributes from the submission table in the DB.
Recommendation: place the function to create a connection into a function.
```{r getThisMonthsAttributeVolume}
tryCatch( {
    message("Trying to connect to database.")
    con <- dbConnect(odbc(), 
                   Driver = "SQL Server", 
                   Server = "ocdb01", 
                   Database = "Population_Segmentation", 
                   Trusted_Connection = "True")
  }, error=function(cond) {
    message("Connection to database failed.")
    message("This means that the workforce data has not been sent to the OPEL database today.")
    message(cond)
    return(NA) 
  }, finally={
    message("Connection to database success.")
    print(con)
  })
thisMonthsMetrics = processASubmissionFile(thisMonthsSubmissionDBTable)
# Change the name of the column from "attrib_YYYMM_complete" to "thisMonth"
names(thisMonthsMetrics)[names(thisMonthsMetrics) == thisMonthsSubmissionDBTable] <- "thisMonth"
```


Join the results from this month with the table of stats (mean, min, max).
```{r performJoin}
message(paste("Rows before join are:", nrow(submissionVolumes), " and columns ", ncol(submissionVolumes)))
submissionVolumes = left_join(thisMonthsMetrics,submissionVolumes, "Attributes")
message(paste("Rows after join are:", nrow(submissionVolumes), " and columns ", ncol(submissionVolumes)))
message("Number of columns should have increased by 1.")
```

Now check how this months attribute volumes compare to history.
Move "This_Month" column to be 5th from the end.

Now calculate the minimum and maximum value for each attribute. We need to calculate a minimum that is
above zero.

```{r calculatePrevelance}
# Create a results of prevalence
tableForScrutiny_prev  = apply(submissionVolumes[,-1],2,function(x){x/sum(x,na.rm=TRUE)})
tableForScrutiny_prev = as.data.frame(tableForScrutiny_prev)
tableForScrutiny_prev$Attributes = thisMonthsMetrics$Attributes # need to put attributes column back in after calculating prevalence
tableForScrutiny_prev = tableForScrutiny_prev %>% relocate(Attributes) # move to first column
tableForScrutiny_prev$Minimum = apply(tableForScrutiny_prev[,2:ncol(tableForScrutiny_prev)], 1, function(x) min(x[x>0], na.rm=TRUE))
tableForScrutiny_prev$Maximum = apply(tableForScrutiny_prev[,2:ncol(tableForScrutiny_prev)], 1, function(x) max(x[x>0], na.rm=TRUE))
tableForScrutiny_prev$Mean = apply(tableForScrutiny_prev[,2:ncol(tableForScrutiny_prev)], 1, function(x) mean(x[x>0], na.rm=TRUE))
tableForScrutiny_prev$isValid = tableForScrutiny_prev$thisMonth >= tableForScrutiny_prev$Minimum &
  tableForScrutiny_prev$thisMonth <= tableForScrutiny_prev$Maximum
tableForScrutiny_prev = tableForScrutiny_prev %>% relocate(thisMonth, .after = last_col()-4)
tableForScrutiny_prev = percent(tableForScrutiny_prev)
# Convert data to nicely formatted percentage
```

Now calculate actuals
```{r calcActuals}
# column 2 of submissionVolumes stores the attributes for this month so we calculate minimum from 3 onward.
tableForScrutiny = submissionVolumes
tableForScrutiny$Minimum = apply(submissionVolumes[,3:ncol(submissionVolumes)], 1, function(x) min(x[x>0], na.rm=TRUE))
tableForScrutiny$Maximum = apply(submissionVolumes[,3:ncol(submissionVolumes)], 1, function(x) max(x[x>0], na.rm=TRUE))
tableForScrutiny$Mean = apply(submissionVolumes[,3:ncol(submissionVolumes)], 1, function(x) mean(x[x>0], na.rm=TRUE))

tableForScrutiny$isValid = tableForScrutiny$thisMonth >= tableForScrutiny$Minimum &
  tableForScrutiny$thisMonth <= tableForScrutiny$Maximum
ncol = ncol(tableForScrutiny)
nrow = nrow(tableForScrutiny)
tableForScrutiny = tableForScrutiny %>% relocate(thisMonth, .after = last_col()-4)
```

Write data to csv file to eye ball.  Look if there are any FALSE in the ISVALID column and try and understand
why before you submit the file.  
```{r writeDataToCSV}
write.csv(tableForScrutiny, paste0("./areAttributesReadyToSubmit/areAttributesReadyToSubmit_actuals", today(), ".csv"), row.names=FALSE)
write.csv(tableForScrutiny_prev, paste0("./areAttributesReadyToSubmit/areAttributesReadyToSubmitprevalence", today(), ".csv"), row.names=FALSE)
```

