---
title: "Validate PHM"
author: "Philip Gladwin"
date: "05/08/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## PHM Validator
This code is designed to be run after all the data relevant to PHM has been extracted from EMIS and
before it is uploaded to the database using the SQL code.
Its aims are to highlight any problems with the set of data before the SQL code is executed.  This may be:-
1. Missing files
2. Files with headers
3. Files with the wrong 'relevant start date'
4. Duplicated files
5. Files which have too few rows
6. Files with the wrong number of columns
7. To check they are in csv format

The steps in this code are:
1. To read in the csv files
2. Validate them against the above criteria
3. Stop the code and alert the user if a problem is found.  The problem can then be solved manually
and this code re-run.

Inputs to the code:
There is only one input to the code and that is a reference to the month you are working on e.g. '202008'

# Improvements:
1. validate that the bp_date_reading relative run date was set to last day of month.  
I think the check to do this is that there is only the one month in the date column.
2. Check the if a file has a date column that we check that the dates are not in the future, not in the past and not silly

# Tasks completed
1. Write some code in R which lists the files which need to be executed in group1, group2, ..
group 7...because they did not run in all_groups.  Doing this manually causes 
delays.

```{r init}
library(pracma)
library(tools)
library(stringr)
library(tidyverse)
library(logger)
library(assertthat)
```
Inputs
```{r inputs}
asOfMonth = '202202' # CHANGE ME
```


# Activity data validation
```{r activityPrep}
firstOfCurrentMonth = as.Date(paste0("01-", substring(asOfMonth,5,7), "-", substring(asOfMonth,1,4)), format("%d-%m-%Y"))
firstOfNextMonth = firstOfCurrentMonth + months(1)
activityPath = paste0("Z:\\Population Health Management\\Activity Data\\processing_folder\\Raw_Data\\", asOfMonth)
appsPath = paste0(activityPath, "\\Appointments")
consPath = paste0(activityPath, "\\Consultations")
pxPath = paste0(activityPath, "\\Px")
asOfMonthsAsMonth = substring(asOfMonth,first = 5,9)
```
For activity check that all files have been downloaded.
```{r checkAppointments}
app_templateFilenames = 
  c("PHM_Act_Appointments_G1.csv",
    "PHM_Act_Appointments_G2.csv",
    "PHM_Act_Appointments_G3.csv",
    "PHM_Act_Appointments_G4.csv",
    "PHM_Act_Appointments_G5.csv",
    "PHM_Act_Appointments_G6.csv",
    "PHM_Act_Appointments_G7.csv")

appfileNames = rownames(file.info(list.files(path=appsPath,pattern="\\.csv$", full.names=FALSE)))

haveAllAppsBeenDownloaded = app_templateFilenames %in% appfileNames
temp = app_templateFilenames[haveAllAppsBeenDownloaded==FALSE]
assert_that(sum(haveAllAppsBeenDownloaded)==length(app_templateFilenames), 
            msg = paste0("Not all the appointment files have been downloaded in path ", 
                         appsPath, ".  Check for missing files and run this code again.  Missing file(s) are ", temp))

haveTooManyAppsBeenDownloaded =  appfileNames %in% app_templateFilenames

temp = appfileNames[haveTooManyAppsBeenDownloaded==FALSE]
assert_that(length(temp) == 0, 
          msg = paste0("Too many files have been downloaded in path ", 
                         appsPath, ".  Delete those files and run this code again.  Extra file(s) are ", temp))

```

Now check consultations:
```{r checkConsultations}
cons_templateFilesnames = c(
  "PHM_Act_Consultations_a1_G1.csv",
  "PHM_Act_Consultations_a1_G2.csv",
  "PHM_Act_Consultations_a1_G3.csv",
  "PHM_Act_Consultations_a1_G4.csv",
  "PHM_Act_Consultations_a1_G5.csv",
  "PHM_Act_Consultations_a1_G6.csv",
  "PHM_Act_Consultations_a1_PMG_FN_G6.csv",
  "PHM_Act_Consultations_a1_PMG_MU_G6.csv",
  "PHM_Act_Consultations_a1_G7.csv",
  "PHM_Act_Consultations_a2_G1.csv",
  "PHM_Act_Consultations_a2_G2.csv",
  "PHM_Act_Consultations_a2_G3.csv",
  "PHM_Act_Consultations_a2_G4.csv",
  "PHM_Act_Consultations_a2_G5.csv",
  "PHM_Act_Consultations_a2_G6.csv",
  "PHM_Act_Consultations_a2_G7.csv",
  "PHM_Act_Consultations_a3_G1.csv",
  "PHM_Act_Consultations_a3_G2.csv",
  "PHM_Act_Consultations_a3_G3.csv",
  "PHM_Act_Consultations_a3_G4.csv",
  "PHM_Act_Consultations_a3_G5.csv",
  "PHM_Act_Consultations_a3_G7.csv",
  "PHM_Act_Consultations_a4_G1.csv",
  "PHM_Act_Consultations_b1_G1.csv",
  "PHM_Act_Consultations_b1_G2.csv",
  "PHM_Act_Consultations_b1_G3.csv",
  "PHM_Act_Consultations_b1_G4.csv",
  "PHM_Act_Consultations_b1_G5.csv",
  "PHM_Act_Consultations_b1_G6.csv",
  "PHM_Act_Consultations_b1_G7.csv",
  #"PHM_Act_Consultations_b2_G1.csv",
  "PHM_Act_Consultations_b2_G1_ET_CS.csv",
  "PHM_Act_Consultations_b2_G1_SV_GR.csv",
  "PHM_Act_Consultations_b2_G2.csv",
  #"PHM_Act_Consultations_b2_G3.csv",
  "PHM_Act_Consultations_b2_G3_CH_GR_HS.csv",
  "PHM_Act_Consultations_b2_G3_LH_PS_OS.csv",
  "PHM_Act_Consultations_b2_G4.csv",
  "PHM_Act_Consultations_b2_G5.csv",
  "PHM_Act_Consultations_b2_G6.csv",
  "PHM_Act_Consultations_b2_FW_G6.csv",
  "PHM_Act_Consultations_b2_G7.csv",
  "PHM_Act_Consultations_b3_G1.csv",
  "PHM_Act_Consultations_b3_G2.csv",
  "PHM_Act_Consultations_b3_G4.csv",
  "PHM_Act_Consultations_b3_G5.csv",
  "PHM_Act_Consultations_b3_G6.csv",
  "PHM_Act_Consultations_b3_G7Crest.csv",
  "PHM_Act_Consultations_b3_G7Tyntsfield.csv"
  )

consfileNames = rownames(file.info(list.files(path=consPath,pattern="\\.csv$", full.names=FALSE)))

# Check for missing files
haveAllConsBeenDownloaded = cons_templateFilesnames %in% consfileNames
a_msg = paste0("These files are missing: ", cons_templateFilesnames[haveAllConsBeenDownloaded==FALSE], collapse = "")
assert_that(sum(haveAllConsBeenDownloaded)==length(cons_templateFilesnames), msg = a_msg)
              

# Have more files been downloaded than we need?
moreConsFilesThanNeeded = consfileNames %in% cons_templateFilesnames
temp = consfileNames[moreConsFilesThanNeeded==FALSE]
assert_that(length(temp)==0, msg=paste0("More files have been downlaoded than we need: ", consfileNames[moreConsFilesThanNeeded==FALSE]))
```

Finally check prescriptions:
```{r checkPrescriptions}
px_TemplateFilesnames = c(
  "PHM_Px_Extract_G3.csv",
  "PHM_Px_Extract_G4.csv",
  "PHM_Px_Extract_G5F.csv",
  "PHM_Px_Extract_G5M.csv",
  "PHM_Px_Extract_a1_G1.csv",
  "PHM_Px_Extract_a1_G2.csv",
  "PHM_Px_Extract_a1_G7.csv",
  "PHM_Px_Extract_a2_G1.csv",
  "PHM_Px_Extract_a2_G2.csv",
  "PHM_Px_Extract_a2_G7.csv",
  "PHM_Px_Extract_G6.csv")

pxfileNames = rownames(file.info(list.files(path=pxPath,pattern="\\.csv$", full.names=FALSE)))

haveAllPxBeenDownloaded = px_TemplateFilesnames %in% pxfileNames

m = paste0("These files are missing: ", px_TemplateFilesnames[haveAllPxBeenDownloaded==FALSE], ".")
m = paste0(m, "Check for missing files and run this code again.")
assert_that(sum(haveAllPxBeenDownloaded)==length(px_TemplateFilesnames), msg=m)

#if (sum(haveAllPxBeenDownloaded)!=length(px_TemplateFilesnames)) {
#  message()
#  message("These files are missing", px_TemplateFilesnames[haveAllPxBeenDownloaded==FALSE])
#  stop(paste0("Not all the px files have been downloaded in path ", pxPath, "  Check for missing files and run this code again."))
#}

# Have more files been downloaded than we need?
morePxFilesThanNeeded = pxfileNames %in% px_TemplateFilesnames
m = paste0("More files have been downloaded than we need.", pxfileNames[morePxFilesThanNeeded==FALSE])
m = paste0(m, "Correct this and then re-run the code.")
temp = pxfileNames[morePxFilesThanNeeded==FALSE]
assert_that(isempty(temp)==TRUE, msg=m)
```

# Appointments
Checks
1. All L8 codes. Not done.
2. Correct number of columns. Done.
3. More than X 1000 rows. Done.
4. Appointment date is the month in question only.  No other months.  Done.
```{r checkAppointments}
message("Working on activity appointments.")
fullList = ""
for (i in 1:length(app_templateFilenames)) {
  log_info("File: {i} of {length(app_templateFilenames)}  {app_templateFilenames[i]}")
  f = read.csv(paste0(appsPath, "\\", app_templateFilenames[i]), stringsAsFactors = FALSE)
  assert_that(ncol(f) == 13 & nrow(f) > 10000, msg = paste0("Not enough rows or columns in file: ", app_templateFilenames[i], ".  Check the file and correct it and run this code again."))
  
  
  f$Appointment.Date = as.Date(f$Appointment.Date, "%d-%b-%Y")
  asMonths = format(f$Appointment.Date,"%m")
  if ((as.numeric(min(asMonths, na.rm=TRUE)) != as.numeric(asOfMonthsAsMonth))
      && (as.numeric(max(asMonths, na.rm=TRUE)) != as.numeric(asOfMonthsAsMonth))) {
    message(paste0("We are looking for the month of ", asOfMonthsAsMonth, " but have found some dates outside that range.  Check file ", app_templateFilenames[i])) 
  }
}
```
# Consultations
1. All L8 codes
2. Correct number of columns
3. More than X 1000 rows
4. Appointment date is the month in question only.  No other months
```{r WorkingOnConsultations}
message("Working on consultations.")
for (i in 1:length(cons_templateFilesnames)) {
  message(paste0("File: ", i, " of ", length(cons_templateFilesnames), " ",  cons_templateFilesnames[i]))
  f = read.csv(paste0(consPath, "\\", cons_templateFilesnames[i]), stringsAsFactors = FALSE)
  if (nrow(f)>1) { 
    assert_that(ncol(f) == 13 & nrow(f) > 10000, msg = paste0("Not enough rows or columns in file: ", cons_templateFilesnames[i], ".  Check the file and correct it and run this code again."))
    
    f$Date = as.Date(f$Date, "%d-%b-%Y")
    asMonths = format(f$Date,"%m")
    if ((as.numeric(min(asMonths, na.rm=TRUE)) != as.numeric(asOfMonthsAsMonth))
        && (as.numeric(max(asMonths, na.rm=TRUE)) != as.numeric(asOfMonthsAsMonth))) {
      message(paste0("We are looking for the month of ", asOfMonthsAsMonth, " but have found some dates outside that range.  Check file ", cons_templateFilesnames[i])) 
    }
  } else {
    log_warn("The file is probably empty and contains 'This report is empty'")
    log_warn("There are zero rows in file: {cons_templateFilesnames[i]}.  Check this is correct.  It's fine if it is correct.")
  }
}
```


# Prescriptions
1. All L8 codes
2. Correct number of columns
3. More than X 1000 rows
4. Appointment date is the month in question only.  No other months
```{r checkPrescriptions}
message("Working on prescriptions.")
for (i in 1:length(px_TemplateFilesnames)) {
  message(paste0("File: ", i, " of ", length(px_TemplateFilesnames), " ",  px_TemplateFilesnames[i]))
  f = read.csv(paste0(pxPath, "\\", px_TemplateFilesnames[i]), stringsAsFactors = FALSE)
  ## NOTE: Need to bring this up in a meeting.  The file only has 7 columns but R thinks
  ## it has 8.
  
  assert_that(ncol(f) == 8 & nrow(f) > 10000, msg = paste0("Not enough rows or columns in file: ", px_TemplateFilesnames[i], ".  Check the file and correct it and run this code again."))
 
  f$Date = as.Date(f$Date, "%d-%b-%Y")
  asMonths = format(f$Date,"%m")
  if ((as.numeric(min(asMonths, na.rm=TRUE)) != as.numeric(asOfMonthsAsMonth))
      && (as.numeric(max(asMonths, na.rm=TRUE)) != as.numeric(asOfMonthsAsMonth))) {
    message(paste0("We are looking for the month of ", asOfMonthsAsMonth, " but have found some dates outside that range.  Check file ", px_TemplateFilesnames[i])) 
  }
}
```



