
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r init}
library(pracma)
library(logger)
library(tools)
library(stringr)
library(tidyverse)
asOfMonth = '202202'
pathToPHMFiles = 'Z:\\Population Health Management\\Attributes Data\\processing_folder\\Raw_Data\\'
```

## Check Main demo - the demographic information
We check
1. That there are more than 1 row and 1 column
2. That the header file has not been included
3. That each file exists


Check the demographic files.  Look for the correct number of files and if the files contain column headers.
```{r checkDemographics}
definitiveDemographicList = read.csv("./DefinitionFiles/definitiveDemographicListOfFiles.csv", stringsAsFactors = FALSE)
demographicFiles = file.info(list.files(path=paste0(pathToPHMFiles, asOfMonth,"\\Main_Demo"),pattern="\\.csv$", full.names=FALSE))

# Check if there are more or less files than we should have
if (nrow(definitiveDemographicList) != nrow(demographicFiles)) {
  message(paste0("I was expecting ",nrow(definitiveDemographicList), " and got ",  nrow(demographicFiles)))
  message(paste0("missing files are: ", definitiveDemographicList[definitiveDemographicList[,1] %in% rownames(demographicFiles)==FALSE,1]))
  stop("The number of demographic files is not equal to the number in the definitive list of files")
}
dm = rownames(demographicFiles)

check1 = dm %in% definitiveDemographicList[,1]
if (sum(check1)!=nrow(definitiveDemographicList)) {
  message(paste0("Unknown files:", dm[check1==FALSE]))
}

check2 = definitiveDemographicList[,1] %in% dm 
if (sum(check2)!=nrow(definitiveDemographicList)) {
  message(paste0("Missing files:", definitiveDemographicList[check2==FALSE,1]))
}


# Check for column headings
nof = nrow(demographicFiles)
for (i in 1:nof) {
  out = tryCatch( {
      # If the file contains headers then the read.csv file will fail and give the error message that there are
      # more columns than column names
      cat(paste("i = ",i, " ",  rownames(demographicFiles)[i], "\n"))
      fn = paste0(pathToPHMFiles, asOfMonth, "\\Main_Demo\\",  rownames(demographicFiles)[i])
      temp = read.csv(fn, stringsAsFactors = FALSE )
      stopifnot((nrow(temp) > 1 | ncol(temp) > 1))
    },
    error=function(cond) {
            message(paste("File ", fn, "may contain headers in the file."))
            message("Check the file remove the headers and run this code again.")
            message(cond)
            # Choose a return value in case of error
            return(NA)
    }
    )
}
```

Now go and create the merged demographic file as described in the PHM walk-through document and then run this code
```{r checkdemographicsmerged}
# We need to check on the unique number of L8 codes.  Alert team if some L8 codes haven't appeared.
s = paste0("Z:/Population Health Management/Attributes Data/processing_folder/Raw_Data/",asOfMonth,"/Main_Demo/PHM_Demo_Merged_", asOfMonth, ".csv")
demo_merged = read_csv(s, 
              col_types = cols(`Registration Date` = col_date(format = "%d-%b-%Y")))

uniqueL8 = unique(demo_merged$`Usual GP's Organisation Code`)
# Remove NA and "Usual GP's Organisation Code
uniqueL8 = str_remove_all(uniqueL8,"Usual GP's Organisation Code")
uniqueL8 = uniqueL8[nchar(uniqueL8)>5]
uniqueL8 = na.omit(uniqueL8)
uniqueL8
log_info("There are {length(uniqueL8)} unique L8 codes.  Pass this by the team to check it is correct in case a Practice has switched itself off from EMIS.")
log_info("Remember to change the column names in PHM_Demo_Merged_YYYYMM.csv manually.")
write.csv(uniqueL8, file=paste0("Demographic_unique_L8_codes",asOfMonth, ".csv"))
```



